---
title: "Notes to AES Figures"
author: "Jeff Norville"
theme: "simplex"
bibliography: C:/Users/Norville/Documents/Bibliographies/INRA-2018.bib
# bibliography: "C:/Users/Jeff Norville/Documents/Mendeley Bibtex/INRA-2018.bib"
output: 
  pdf_document:
    toc: yes
  html_document:
    toc: yes
link-citations: yes
biblio-style: apalike
---

<!-- remember to install distill at home https://rstudio.github.io/distill/ -->




## Simplified figure

 

```{r Simple fig, message=FALSE, echo=FALSE}
#library(readxl)
library(igraph)

simplinks <- read.csv("../simplifylinks3.csv", sep=";", header=TRUE, stringsAsFactors = FALSE)
simpnodes <- read.csv("../simplifynodes.csv", sep=";", header=TRUE, stringsAsFactors = FALSE)
# net <- graph_from_data_frame(d=simplinks, vertices=simpnodes, directed=TRUE)
# plot(net, layout = layout_with_lgl, label = simpnodes$short.definition)
# plot(net)

# library(networkD3)
# simpNetwork <- data.frame(simplinks$from, simplinks$to)
# simpleNetwork(simpNetwork, fontFamily = "fantasy", zoom=T)



library("visNetwork") 
library(stringr)
vis.simpnodes <- simpnodes
vis.simplinks <- simplinks
vis.simpnodes$shape <- simpnodes$node.type
vis.simpnodes$shape <- str_replace(vis.simpnodes$shape, "challenge", "box")
vis.simpnodes$shape <- str_replace(vis.simpnodes$shape, "solution", "ellipse")
vis.simpnodes$color <- simpnodes$node.type
vis.simpnodes$color <- str_replace(vis.simpnodes$color, "challenge", "lightgrey")
vis.simpnodes$color <- str_replace(vis.simpnodes$color, "solution", "gold")

vis.simpnodes$shadow <- TRUE # Nodes will drop shadow
#vis.simpnodes$label  <- simpnodes$id
vis.simpnodes$label  <- simpnodes$short.definition
vis.simpnodes$title  <- simpnodes$long.definition
vis.simpnodes$borderWidth <- 1 

# vis.simpnodes$color.border <- "black"
# vis.simpnodes$color.highlight.background <- "lightgreen"
# vis.simpnodes$color.highlight.border <- "red"

vis.simplinks$width <- simplinks$weight*3 # line width
vis.simplinks$dashes <- c(FALSE, FALSE, TRUE)[simplinks$color] 
vis.simplinks$color <- c("green", "red", "slategrey")[simplinks$color]  
#vis.simplinks$arrows <- "middle"
vis.simplinks$smooth <- TRUE    # should the edges be curved?
vis.simplinks$shadow <- FALSE    # edge shadow
vis.simplinks$labelHighlightBold <- TRUE

visNetwork(vis.simpnodes, vis.simplinks) %>% 
  visPhysics(solver = "forceAtlas2Based", 
  forceAtlas2Based = list(gravitationalConstant = -10))

```


## Mapping out the D1.1 Table

I've changed to reading in a csv file instead of the Excel directly, as the objects in R really don't appreciate the spaces Excel sometimes obliges.

Table A is now pulls values from Table D1.1, so a change to the text in D1.1 filters through Table A and, with an export, to these figures.

Question for users:
 - I find the arrows redundant to colors
 - in some cases they even conflict
 - the "node:link" architecture forces us to use "direction" (as complex relationships are allowed), but in instances with ? or 0 we don't want an arrow
 - in those cases it's easier to just rely on color
 

```{r AES Figure, message=FALSE, echo=FALSE}
#library(readxl)
library(igraph)


# aes_links <- read_excel("C:/Users/Norville/Dropbox/API-SMAL_Partage_Animation/Livrables/D1.1_List_of_AES_English.xlsm",
#                   sheet = "links", skip = 1)
# aes_nodes <- read_excel("C:/Users/Norville/Dropbox/API-SMAL_Partage_Animation/Livrables/D1.1_List_of_AES_English.xlsm",
#                         sheet = "nodes", skip = 1)

aeslinks <- read.csv("../aeslinks5.csv", sep=";", header=TRUE, stringsAsFactors = FALSE)
aesnodes <- read.csv("../aesnodes5.csv", sep=";", header=TRUE, stringsAsFactors = FALSE)
# net <- graph_from_data_frame(d=aeslinks, vertices=aesnodes, directed=TRUE)
# # plot(net, layout = layout_with_lgl, label = aesnodes$short.definition)
# plot(net)

```

## visNetwork with node ids only 

This layout is easier to zoom in and out to read labels, as well as make link directions more clear. Presenting all links in one diagram is a bit crowded.

```{r All parts, message=FALSE, echo=FALSE}
library("visNetwork") 
library(stringr)
vis.aesnodes <- aesnodes
vis.aeslinks <- aeslinks
vis.aesnodes$shape <- aesnodes$node.type
vis.aesnodes$shape <- str_replace(vis.aesnodes$shape, "challenge", "box")
vis.aesnodes$shape <- str_replace(vis.aesnodes$shape, "solution", "ellipse")
vis.aesnodes$color <- aesnodes$node.type
vis.aesnodes$color <- str_replace(vis.aesnodes$color, "challenge", "lightgrey")
vis.aesnodes$color <- str_replace(vis.aesnodes$color, "solution", "gold")

vis.aesnodes$shadow <- TRUE # Nodes will drop shadow

#vis.aesnodes$label["node.type"=="challenge"] <- aesnodes$short.definition

vis.aesnodes$label  <- aesnodes$id
# vis.aesnodes["label"=="n900"] <- "Biodiversity"
# vis.aesnodes["label"=="n906"] <- "Targeted biodiversity"

vis.aesnodes$title  <- aesnodes$short.definition
vis.aesnodes$borderWidth <- 1 

# vis.aesnodes$color.border <- "black"
# vis.aesnodes$color.highlight.background <- "lightgreen"
# vis.aesnodes$color.highlight.border <- "red"

vis.aeslinks$width <- aeslinks$weight*3 # line width
vis.aeslinks$dashes <- c(FALSE, FALSE, TRUE)[aeslinks$color] 
vis.aeslinks$color <- c("green", "red", "slategrey")[aeslinks$color]  
#vis.aeslinks$arrows <- "middle"
vis.aeslinks$smooth <- FALSE    # should the edges be curved?
vis.aeslinks$shadow <- FALSE    # edge shadow
vis.aeslinks$labelHighlightBold <- TRUE



visNetwork(vis.aesnodes, vis.aeslinks)
```


Same diagram with short names shown:

```{r All parts longer description, message=FALSE, echo=FALSE}

#should test labels on challenge items as long.def?
vis.aesnodes$label  <- aesnodes$short.definition

visNetwork(vis.aesnodes, vis.aeslinks)
```



## Crop / Culture Choice
```{r Crop Choice, message=FALSE, echo=FALSE}
library(dplyr)
# ccnodes <- read.csv("../cropchoicenodes.csv", sep=";", header=TRUE, as.is = TRUE) # stringsAsFactors = FALSE
# cclinks <- read.csv("../cropchoicelinks.csv", sep=";", header=TRUE, as.is = TRUE)

ccnodes <- select(filter(aesnodes,  com_solution %in% c("Crop choice",
                                                   "Biodiversity", 
                                                   "Targeted biodiversity", 
                                                   "Crop protection", 
                                                   "GHG Emissions", 
                                                   "Pollution", 
                                                   "Soil fertility",
                                                   "Production")),
               c(id, node.type, com_solution, short.definition, long.definition, node.type.id))

cclinks <- select(filter(aeslinks,  group == "Crop choice"),
               c(from, to, group, challenge, label, color, weight))

# head(aesnodes)

vis.cclinks <- cclinks
vis.ccnodes <- ccnodes

# visNetwork(vis.ccnodes, vis.cclinks) 
vis.ccnodes$shadow <- FALSE # Nodes will drop shadow
vis.ccnodes$title  <- ccnodes$long.definition
vis.ccnodes$label  <- ccnodes$short.definition
vis.ccnodes$borderWidth <- 1 # Node border width
vis.ccnodes$shape <- ccnodes$node.type
vis.ccnodes$shape <- str_replace(vis.ccnodes$shape, "challenge", "box")
vis.ccnodes$shape <- str_replace(vis.ccnodes$shape, "solution", "ellipse")
vis.ccnodes$color <- ccnodes$node.type
vis.ccnodes$color <- str_replace(vis.ccnodes$color, "challenge", "lightgrey")
vis.ccnodes$color <- str_replace(vis.ccnodes$color, "solution", "gold")

vis.ccnodes$color.border <- "black"
# vis.ccnodes$color.highlight.background <- "lightgreen"
# vis.ccnodes$color.highlight.border <- "red"

# edges
vis.cclinks$color <- c("green", "red", "slategrey")[cclinks$color] 
vis.cclinks$width <- cclinks$weight*4 # line width
vis.cclinks$dashes <- c(FALSE, FALSE, TRUE)[cclinks$color] 
vis.cclinks$smooth <- TRUE    # should the edges be curved?
vis.cclinks$shadow <- FALSE    # edge shadow
#vis.cclinks$color <- c("green", "red")[cclinks$color] #line color  

visNetwork(vis.ccnodes, vis.cclinks) 


```


### Choice of cultures, impact on nitrate loading


Relative to mineral fertilization, @Tahat2020 cites studies on organic farms showing 50\% increases in nitrogen supply and sequestration capacity through planting of leguminous crops such as peas or alfalfa. 

A mix of legume and livestock production is identified in @Luscher2014 as an optimal production system to meet increasing demand for meat in the European markets. Specifically a 30 - 50\% legume crop is found to augment forage, reduce inorganic fertilizer dependency, and aid in mitigating \ce{CO2} emissions.

In a study of three fertilizer systems (conventional, legume-fed cattle manure, and legume-biomass based), nitrogen leaching was found to be highest in the conventional system by 50\% (@Drinkwater1998). 


### Choice of cultures, impact on biodiversity

In their 2011 study of the influence on European farmland species diversity decline, @Kleijn2011 posed four questions (paraphrased):
    1. How do conservation initiatives impact species?
    2. Do local conservation initiatives scale up to national or continental trends, and how?
    3. Can we distinguish population-level response from behavioral response to conservation initiatives?
    4. Are conservation initiatives effective for target species in changing agricultural landscapes?


Of the few N American efforts in our review of upscaling from the farm plot to the landscape, @Wilson2017 divided agricultural land use in two, separating forage (hay, alfalfa) from all other arable crops (including oilseeds, cereals, grains and pulses). 





## Increase varietal diversity
```{r Varietal choice, message=FALSE, echo=FALSE}
varchoicenodes <- select(filter(aesnodes,  com_solution %in% c("Varietal choice",
                                                   "Biodiversity", 
                                                   "Targeted biodiversity", 
                                                   "Crop protection", 
                                                   "GHG Emissions", 
                                                   "Pollution", 
                                                   "Soil fertility",
                                                   "Production")),
               c(id, node.type, com_solution, short.definition, long.definition, node.type.id))

varchoicelinks <- select(filter(aeslinks,  group == "Varietal choice"),
               c(from, to, group, challenge, label, color, weight))

vis.varchoicenodes <- varchoicenodes
vis.varchoicelinks <- varchoicelinks

vis.varchoicenodes$shape <- varchoicenodes$node.type
vis.varchoicenodes$shape <- str_replace(vis.varchoicenodes$shape, "challenge", "box")
vis.varchoicenodes$shape <- str_replace(vis.varchoicenodes$shape, "solution", "ellipse")
vis.varchoicenodes$color <- varchoicenodes$node.type
vis.varchoicenodes$color <- str_replace(vis.varchoicenodes$color, "challenge", "lightgrey")
vis.varchoicenodes$color <- str_replace(vis.varchoicenodes$color, "solution", "gold")
vis.varchoicenodes$shadow <- FALSE # Nodes will drop shadow
vis.varchoicenodes$title  <- varchoicenodes$long.definition
vis.varchoicenodes$label  <- varchoicenodes$short.definition
vis.varchoicenodes$borderWidth <- 1 # Node border width
vis.varchoicenodes$color.background <- c("gold", "grey")[varchoicenodes$node.type]
vis.varchoicenodes$color.border <- "black"
# vis.varchoicenodes$color.highlight.background <- "lightgreen"
# vis.varchoicenodes$color.highlight.border <- "red"

# edges
vis.varchoicelinks$width <- varchoicelinks$weight*4 # line width
vis.varchoicelinks$color <- c("green", "red", "slategrey")[varchoicelinks$color] #  
vis.varchoicelinks$dashes <- c(FALSE, FALSE, TRUE)[varchoicelinks$color] 

# vis.varchoicelinks$arrows <- "middle" # arrows: 'from', 'to', or 'middle'
vis.varchoicelinks$smooth <- TRUE    # should the edges be curved?
vis.varchoicelinks$shadow <- FALSE    # edge shadow

visNetwork(vis.varchoicenodes, vis.varchoicelinks)

```


### When discussing Varietal diversity / intra-plot genetics (varietal association)

Rethinking criteria for measuring performance of varieties will be an important change; per @Barot2017, ecologists and agronomists currently use tools to measure interactions between varieties rather than opportunities of synergies.

"Mixture performance should therefore be compared to the performance of the pure variety that would have been chosen by the farmer in this field."

Examples: Diversity of plant, invertebrate (arthropod) and animal (ex farm birds) life.



## Forest
```{r Forest, message=FALSE, echo=FALSE}
library(dplyr)
library(stringr)
forestnodes <- select(filter(aesnodes,  com_solution %in% c("Forest",
                                                   "Biodiversity", 
                                                   "Targeted biodiversity", 
                                                   "Crop protection", 
                                                   "GHG Emissions", 
                                                   "Pollution", 
                                                   "Soil fertility",
                                                   "Production")),
               c(id, node.type, com_solution, short.definition, long.definition, node.type.id))

forestlinks <- select(filter(aeslinks,  group == "Forest"),
               c(from, to, group, challenge, label, color, weight))

vis.forestnodes <- forestnodes
vis.forestlinks <- forestlinks

vis.forestnodes$shape <- forestnodes$node.type
vis.forestnodes$shape <- str_replace(vis.forestnodes$shape, "challenge", "box")
vis.forestnodes$shape <- str_replace(vis.forestnodes$shape, "solution", "ellipse")
vis.forestnodes$color <- forestnodes$node.type
vis.forestnodes$color <- str_replace(vis.forestnodes$color, "challenge", "lightgrey")
vis.forestnodes$color <- str_replace(vis.forestnodes$color, "solution", "gold")

vis.forestnodes$shadow <- FALSE # Nodes will drop shadow
vis.forestnodes$title  <- forestnodes$long.definition
vis.forestnodes$label  <- forestnodes$short.definition
vis.forestnodes$borderWidth <- 1 # Node border width
vis.forestnodes$color.border <- "black"
# vis.forestnodes$color.highlight.background <- "lightgreen"
# vis.forestnodes$color.highlight.border <- "red"

# edges
vis.forestlinks$width <- forestlinks$weight*4 # line width
vis.forestlinks$color <- c("green", "red", "slategrey")[forestlinks$color]
vis.forestlinks$dashes <- c(FALSE, FALSE, TRUE)[forestlinks$color] 

# vis.forestlinks$arrows <- "middle" # arrows: 'from', 'to', or 'middle'
vis.forestlinks$smooth <- TRUE    # should the edges be curved?
vis.forestlinks$shadow <- FALSE    # edge shadow

visNetwork(vis.forestnodes, vis.forestlinks)
# %>%  visEdges(color = c("green", "red")[forestlinks$color])

```

Sparing larger forests provides increased biodiversity, with exception of bird species (shelter) @Edwards2015



## Infrastructure AE
```{r Infrastructure AE, message=FALSE, echo=FALSE}
library(dplyr)
library(stringr)
iaesnodes <- select(filter(aesnodes,  com_solution %in% c("Infrastructure AE",
                                                   "Biodiversity", 
                                                   "Targeted biodiversity", 
                                                   "Crop protection", 
                                                   "GHG Emissions", 
                                                   "Pollution", 
                                                   "Soil fertility",
                                                   "Production")),
               c(id, node.type, com_solution, short.definition, long.definition, node.type.id))

iaeslinks <- select(filter(aeslinks,  group == "Infrastructure AE"),
               c(from, to, group, challenge, label, color, weight))

vis.iaesnodes <- iaesnodes
vis.iaeslinks <- iaeslinks

vis.iaesnodes$shape  <- iaesnodes$node.type
vis.iaesnodes$shape <- str_replace(vis.iaesnodes$shape, "challenge", "box")
vis.iaesnodes$shape <- str_replace(vis.iaesnodes$shape, "solution", "ellipse")

#vis.iaesnodes$color.background <- c("gold", "grey")[iaesnodes$node.type]
vis.iaesnodes$color <- iaesnodes$node.type
vis.iaesnodes$color <- str_replace(vis.iaesnodes$color, "challenge", "lightgrey")
vis.iaesnodes$color <- str_replace(vis.iaesnodes$color, "solution", "gold")

vis.iaesnodes$shadow <- TRUE # Nodes will drop shadow
vis.iaesnodes$title  <- iaesnodes$long.definition
vis.iaesnodes$label  <- iaesnodes$short.definition
vis.iaesnodes$borderWidth <- 1 # Node border width
vis.iaesnodes$color.border <- "black"

# edges
vis.iaeslinks$color <- c("green", "red", "slategrey")[iaeslinks$color]
vis.iaeslinks$width <- iaeslinks$weight*4 # line width
vis.iaeslinks$dashes <- c(FALSE, FALSE, TRUE)[iaeslinks$color] 

# NB arrows when weight is zero will cause confusion
vis.iaeslinks$smooth <- TRUE    # should the edges be curved?
vis.iaeslinks$shadow <- FALSE    # edge shadow

visNetwork(vis.iaesnodes, vis.iaeslinks)


```

### Sparing vs sharing

According to @Fischer2014, a reframing of the 2005 sharing / sparing framework by Green et al (@Green2005) is due and could look like this (from his list of Recommendations):

    1. Focus on commodity production, not food production, in land scarcity analyses
    2. Recognize limitations: ``\dots partial-trade off analyses cannot directly inform real-world decisions without knowledge on social preferences''
    3. Scale issues: they need to be addressed ore explicitely, and more carefully considered.
    4. Critique has been plentiful, alternatives few: ``A potentially promising approach could be to assess agricultural landscapes as social–ecological systems'' (review how Ostrom 1990 analyzed common property resource systems and its durability)




## Working the soil
```{r Working the soil, message=FALSE, echo=FALSE}

soilnodes <- select(filter(aesnodes,  com_solution %in% c("Working the soil",
                                                   "Biodiversity", 
                                                   "Targeted biodiversity", 
                                                   "Crop protection", 
                                                   "GHG Emissions", 
                                                   "Pollution", 
                                                   "Soil fertility",
                                                   "Production")),
               c(id, node.type, com_solution, short.definition, long.definition, node.type.id))

soillinks <- select(filter(aeslinks,  group == "Working the soil"),
               c(from, to, group, challenge, label, color, weight))

vis.soilnodes <- soilnodes
vis.soillinks <- soillinks

vis.soilnodes$shape  <- soilnodes$node.type
vis.soilnodes$shape <- str_replace(vis.soilnodes$shape, "challenge", "box")
vis.soilnodes$shape <- str_replace(vis.soilnodes$shape, "solution", "ellipse")

#vis.soilnodes$color.background <- c("gold", "grey")[soilnodes$node.type]
vis.soilnodes$color <- soilnodes$node.type
vis.soilnodes$color <- str_replace(vis.soilnodes$color, "challenge", "lightgrey")
vis.soilnodes$color <- str_replace(vis.soilnodes$color, "solution", "gold")

vis.soilnodes$shadow <- FALSE # Nodes will drop shadow
vis.soilnodes$title  <- soilnodes$long.definition
vis.soilnodes$label  <- soilnodes$short.definition
vis.soilnodes$borderWidth <- 1 # Node border width
vis.soilnodes$color.background <- c("gold", "grey")[soilnodes$node.type]
vis.soilnodes$color.border <- "black"
# vis.soilnodes$color.highlight.background <- "lightgreen"
# vis.soilnodes$color.highlight.border <- "red"

# edges
vis.soillinks$width <- soillinks$weight*4 # line width
vis.soillinks$color <- c("green", "red", "slategrey")[soillinks$color] #"green"    # line color
vis.soillinks$dashes <- c(FALSE, FALSE, TRUE)[soillinks$color] 

vis.soillinks$smooth <- TRUE    # should the edges be curved?
vis.soillinks$shadow <- FALSE    # edge shadow

visNetwork(vis.soilnodes, vis.soillinks) 

```




## Discussion



=======

## References


