---
title: "Notes to AES Figures"
author: "Jeff Norville"
bibliography: C:/Users/Norville/Documents/Bibliotheque/INRA-2018.bib
output: 
  html_document:
    toc: yes
  pdf_document:
    toc: yes
link-citations: yes
biblio-style: apalike
---

## Reading in the D1.1 Table

I've changed to reading csv files in, as the objects in R really don't appreciate the spaces Excel sometimes obliges.

Second -- the "from/to" design is designed to help use arrows, but now I realise arrows will obscure the green / red idea -- which seems important, particularly in the meta-images.


```{r message=FALSE}
library(readxl)
library(igraph)


# aes_links <- read_excel("C:/Users/Norville/Dropbox/API-SMAL_Partage_Animation/Livrables/D1.1_List_of_AES_English.xlsm",
#                   sheet = "links", skip = 1)
# aes_nodes <- read_excel("C:/Users/Norville/Dropbox/API-SMAL_Partage_Animation/Livrables/D1.1_List_of_AES_English.xlsm",
#                         sheet = "nodes", skip = 1)

aeslinks <- read.csv("../aeslinks.csv", sep=";", header=TRUE, stringsAsFactors = FALSE)
aesnodes <- read.csv("../aesnodes.csv", sep=";", header=TRUE, stringsAsFactors = FALSE)
net <- graph_from_data_frame(d=aeslinks, vertices=aesnodes, directed=T) 
plot(net)


```


## Forest - not too pretty
```{r}

library(igraph)

forestnodes <- read.csv("../forestnodes.csv", sep=";", header=TRUE, as.is = TRUE) # stringsAsFactors = FALSE
forestlinks <- read.csv("../forestlinks.csv", sep=";", header=TRUE, as.is = TRUE)
net <- graph_from_data_frame(d=forestlinks, vertices=forestnodes, directed=T) 
plot(net)



```

## Forest via visNetwork
```{r}

library("visNetwork") 
vis.forestnodes <- forestnodes
vis.forestlinks <- forestlinks

vis.forestnodes$shape  <- c("ellipse", "box")[forestnodes$node.type]
vis.forestnodes$shadow <- FALSE # Nodes will drop shadow
vis.forestnodes$title  <- forestnodes$node.name
vis.forestnodes$label  <- forestnodes$node.name
vis.forestnodes$borderWidth <- 1 # Node border width
vis.forestnodes$color.background <- c("gold", "grey")[forestnodes$node.type]
vis.forestnodes$color.border <- "black"
vis.forestnodes$color.highlight.background <- "lightgreen"
vis.forestnodes$color.highlight.border <- "red"

# edges
vis.forestlinks$width <- forestlinks$weight*4 # line width
vis.forestlinks$color <- c("green", "red")[forestlinks$color] #"green"    # line color  
vis.forestlinks$arrows <- "middle" # arrows: 'from', 'to', or 'middle'
vis.forestlinks$smooth <- TRUE    # should the edges be curved?
vis.forestlinks$shadow <- FALSE    # edge shadow



visNetwork(vis.forestnodes, vis.forestlinks) %>%
  visEdges(color = c("green", "red")[forestlinks$color])


```







## Discussion

Still having trouble with line color, arrows and labels on ligns are correct. Widths are proportionate to "weight".

I'll add figures for the D1.1 table inline here, then we can collaberate in-line below.

Can I add datatables too?

=======

Practice a citation like @Bayer2019


